Domain Decomposed Monte Carlo

### 2013-02-06 doc/presentations/meeting_2_6_13/meeting_2_6_13.tex
updated my comm param png
adding communication figure

  \begin{itemize}
  \item No literature observed for parallel Neumann-Ulam solvers
    \medskip \medskip
  \item Numerous references for modern parallel Monte Carlo methods in
    reactor physics
    \medskip \medskip
  \item Build a strategy for applying modern methods to the
    Neumann-Ulam method
  \end{itemize}

@@

  \begin{itemize}
  \item Each parallel process owns a piece of the domain
  \item Random walks must be transported across domains through
    communication
  \end{itemize}

  \medskip \medskip
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {Brunner's Work (2006 and 2009)}

    \begin{itemize}
    \item Looked at 4 communication patterns:
      \begin{itemize}
      \item Fully-locking synchronous
      \item Asynchronous-send/synchronous-receive
      \item Master/slave
      \item Binary tree master/slave
      \end{itemize}
    \item Binary tree master/slave performed best but race conditions observed
    \item A later improvement to their work showed a fully asynchronous
      pattern to work best
    \item Poor scaling for unbalanced problems for all schemes
    \end{itemize}

  \end{beamerboxesrounded}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Domain Decomposition}
\end{frame}

%%---------------------------------------------------------------------------%%
\begin{frame}{Fully Synchronous Algorithm}
\end{frame}

%%---------------------------------------------------------------------------%%
\begin{frame}{Fully Asynchronous Algorithm}
\end{frame}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=5in]{my_params.png}
    \end{center}
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=4in]{my_strong.png}
    \end{center}
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=4in]{my_weak.png}
    \end{center}
  \end{figure}

>>>>

  \begin{itemize}
  \item No literature observed for domain decomposed Neumann-Ulam
    solvers; parallelism over histories only (domain replication)
    \medskip \medskip
  \item Numerous references for modern parallel Monte Carlo methods in
    reactor physics
    \medskip \medskip
  \item Build a strategy for applying modern methods to the
    Neumann-Ulam method
  \item New implementation based on the Shift Monte Carlo code
  \end{itemize}

@@

  \begin{itemize}
  \item Each parallel process owns a piece of the domain
  \item Random walks must be transported across domains through
    communication
  \item Brunner and Brantley, \textit{An efficient, robust, domain
    decomposition algorithm for particle Monte Carlo}, Journal of
    Computational Physics, 2009
  \end{itemize}

  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{1.0}{ \input{procassini_example.pdftex_t} }
    \end{center}
  \end{figure}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Domain Decomposition Parallelism}

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=3.75in]{domain_comm.png}
    \end{center}
  \end{figure}

%%---------------------------------------------------------------------------%%
\begin{frame}{Fully Synchronous Algorithm}

  Do until all histories completed on all procs:

  \begin{enumerate}
  \item All local histories transported to local completion
    \begin{itemize}
    \item Histories are buffered in the send buffer
    \item The send buffer has no size limit
    \end{itemize}
  \item Fully locking communication to determine the end of local
    transport
    \medskip
    \begin{itemize}
    \item If send buffers are not empty: fully locking communication
      of send buffers to receive buffers
    \item If they are empty, fully locking communication to end transport
    \end{itemize}
  \end{enumerate}

%%---------------------------------------------------------------------------%%
\begin{frame}{Fully Asynchronous Algorithm}

  Do until all histories completed on all procs:

  \begin{enumerate}
  \item Specified number of histories transported to local completion
    (check frequency)
    \begin{itemize}
    \item If at check frequency, non-locking receive buffers
    \item Any locally terminated histories non-locking communicated to
      the master
    \item Histories are buffered in the send buffers as needed
    \item The send buffer has a size limit (max buffer size)
    \item If any buffer is full, non-locking send it
    \end{itemize}
    \medskip
  \item Master non-locking check for completed histories
    \begin{itemize}
    \item If completed total on master sums to total source
      histories, send non-locking complete message
    \end{itemize}
  \end{enumerate}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=4.75in]{my_params.png}
    \end{center}
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=3.5in]{my_strong.png}
    \end{center}
  \end{figure}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics[width=3in]{my_weak.png}
    \end{center}
  \end{figure}
